Spontaneous Similarity Judgments of Musical Tones played with various Playing Techniques

### 2018-01-25 paper/lagrangeSpontaneousSimilarity2017.tex
done vi1
trivial commit to test version control
comprehend -> understand

Being perceptively defined, musical timbre is an interesting notion to study to better comprehend human auditory perception \cite{grey1977multidimensional}. Thus, by studying musical timbre, one study many facets of the human auditory system which responds to a diverse but also controled and well documented set of physical stimuli. Indeed, this diversity can be more easily controlled than other stimuli such as speech or environmental sounds.

@@

\begin{figure}
\center
\includegraphics[width = \textwidth]{figures/groupInstruments.png}
\caption{Computational model composed of two successive processing stages.}
\label{fig:model}
\end{figure}

>>>>

Being perceptively defined, musical timbre is an interesting notion to study to better understand human auditory perception \cite{grey1977multidimensional}. Thus, by studying musical timbre, one study many facets of the human auditory system which responds to a diverse but also controled and well documented set of physical stimuli. Indeed, this diversity can be more easily controlled than other stimuli such as speech or environmental sounds.

@@

\begin{figure}[t]
\center
\includegraphics[width = \textwidth]{figures/spontaneousSimilarity.png}
\caption{Computational model composed of two successive processing stages and alternative implementations.}
\label{fig:model}
\end{figure}
